POMDP comparisons across sigma_m, sigma_g

### 2017-12-28 appendix/appendix.Rmd
harvest & escapement versions
run even longer

```{r libraries, include=FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning=FALSE, dev="CairoPDF", fig.width=7, fig.height=7)
library(tidyverse)
library(gridExtra)
library(ggthemes)
colours <- ptol_pal()(2)
```

@@

```{r eval=FALSE}
dir.create(log_dir)
options(mc.cores=2)

@@

      sarsop(models[[i]]$transition,
             models[[i]]$observation,
             models[[i]]$reward,
             discount = discount,
             precision = 0.00000002,
             timeout = 20000,
             log_dir = log_dir,
             log_data = log_data)
    })
)

@@

@@

>>>>

```{r libraries, include=FALSE, message=FALSE, warning=FALSE}
devtools::install("..")
knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning=FALSE, dev="CairoPDF", fig.width=7, fig.height=7)
library(tidyverse)
library(gridExtra)
library(ggthemes)
colours <- ptol_pal()(2)
```

@@

```{r eval=TRUE}
dir.create(log_dir)
options(mc.cores=9)

@@

      sarsop(models[[i]]$transition,
             models[[i]]$observation,
             models[[i]]$reward,
             discount = discount,
             precision = 0.00000002,
             timeout = 60000,
             log_dir = log_dir,
             log_data = log_data)
    })
)

@@

### Harvest

@@

### Escapement

```{r}
pomdp_policies %>% 
  ggplot(aes(state, escapement, col=policy)) + 
  geom_line()  + 
  coord_cartesian(xlim = c(0,K), ylim = c(0, .8))
```
